The pollination trade-off

### 2018-11-14 paper/manuscript.Rmd
Write data collection protocols for second objective
(ecological variables)

We collected data from eleven coflowering plant communities and their pollinators distributed across three locations, each in a distinct reagion of the Argentinian Pampas. 
These locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and a climate drier as we move inland and westward towards the Pampean Grasslands.
Annual mean temperatures range between 14.8 and 15.8 Celsius. 
In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where due to the lack of available sites, we were only able to sample one restored fragment.
We visited fragments between December 2010 and February 2011.

@@

In each location, we sampled two restored and two agricultural fragments. 
However, due to the lack of available sites in the Flooding Pampas, it was only possible to sample one restored site.
We visited each fragment in November 2010 and February 2011. 
In each of these visits we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.

>>>>

We collected data from eleven coflowering plant communities and their pollinators distributed across three locations, each in a distinct reagion of the Argentinian Pampas. 
These locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and a climate drier as we move inland and westward towards the Pampean Grasslands.
Annual mean temperatures range between 14.8 and 15.8 Celsius. 
In each location, we sampled two restored and two agricultural fragments, except in the Flooding Pampas, where due to the lack of available sites, we were only able to sample one restored fragment.

@@

To obtain data about (*i*) the number of shared pollinators for each species we pooled data from quantitative and qualitative polination networks. 
Qualitative networks were constructed based on two hour observations of floral visits in each fragment. 
Quantitative networks were constructed using two 50 m randomly located transects in each transect. 
We counted and collected all floral visitors found in a 2 m wide strip while walking at a pace of 10 m per minute [@marrero_effect_2014; @memmott_structure_1999]. 
We visited the transects each month between November 2010 and March 2011. 
To obtain(*ii*) plant abundance, we counted all units of floral atraction found during an independent sampling of the same transects used to construct the quantitative visitation networks. 
We also recorded (*iii*) morphological traits that relate to plant type (herb, shrub, climber), life cycle (annual, perennial), flower colouration, and whether the species is native in the study region. 
In addition we used data from the abundance counts 
Finally, to estimate the (*iv*) visit effectiveness, in addition to the visitation networks we need to construct pollen transfer networks. 
To construct the transfer networks we examined the pollen loads present on the collected floral visitors [@marrero_exotic_2017]. 
When the pollen count on an individual animal was estimated to be less than 2,000 grains, we identified every grain to the species level whenever possible and to pollen complexes when it was not. 
When the pollen count was above 2,000 grains, we classified approx. 50% of pollen and total pollen counts were extrapolated [@bosch_plant-pollinator_2009]. 
More details about the study sites, data collection, and laboratory protocols can be found in Marrero *et al.* (2014 and 2017).
In each of these visits we gathered information related to abundance, plant-pollinator visitation, pollen transfer, and pollen deposition.
